Secure Composition of Robust and Optimising Compilers

### 2023-06-14 popl/main.tex
Type fix in def of mon
Typo fix

\begin{definition}[\glsfirst{tms}]\label{def:trace:tmsdef}
  A trace $\trace$ is temporal memory safe ($\trace\in\tmssafe$) iff $\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Dealloc\ \loc;\sandboxtag';\securitytag'}$, $\ev{Use\ \loc\ n;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Alloc\ \loc\ m;\sandboxtag';\securitytag'}$ and $\ev{Use\ \loc\ n;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Dealloc\ \loc;\sandboxtag';\securitytag'}$.
\end{definition}

@@

\paragraph{Monitor for \glsfirst{tms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{alloced}:L,\text{freed}:L\right\} \hspace{0.33cm}%
    \emptyset:=\ \left\{\text{alloced}:\emptyset,\text{freed}:\emptyset\right\}\\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc \mid \absev{Dealloc\ }\loc \mid \absev{Use\ }\loc \mid \absterm\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
  \typerule{tms-uninteresting}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
  }{tms-uninteresting}
  %
  \typerule{tms-abort}{
  }{
    \monitorcheck[]{\tmsmonitor}{\emptyset}{\absterm}
  }{tms-abort}
  %
  \typerule{tms-use}{
    \loc\in\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    \loc\notin\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\cup\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    \loc\notin\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\setminus\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\cup\left\{\loc\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc}
  }{tms-dealloc}
\end{center}
\begin{center}
  \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ with respect to \gls{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc}
  }{tms-alloc-authentic}
  %
  \typerule{tms-dealloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{tms-dealloc-authentic}
  %
  \typerule{tms-use-authentic}{
  }{
    \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
  }{tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{tms-branch-authentic}
  %
  \typerule{tms-binop-authentic}{
  }{
    \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{tms-binop-authentic}
  %
  \typerule{tms-empty-authentic}{
  }{
    \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{tms-empty-authentic}
  %
  \typerule{tms-abort-authentic}{
  }{
    \tmstraceagree[]{\lightning}{\absterm}
  }{tms-abort-authentic}
\end{center}

>>>>

\begin{definition}[\glsfirst{tms}]\label{def:trace:tmsdef}
  A trace $\trace$ is temporal memory safe ($\trace\in\tmssafe$) iff $\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Dealloc\ \loc;\sandboxtag';\securitytag'}$, $\ev{Use\ \loc\ n;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Alloc\ \loc\ m;\sandboxtag';\securitytag'}$ and $\ev{Dealloc\ \loc;\sandboxtag;\securitytag}\not\le_{\trace}\ev{Use\ \loc\ n;\sandboxtag';\securitytag'}$.
\end{definition}

@@

\paragraph{Monitor for \glsfirst{tms}}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{alloced}:L,\text{freed}:L\right\} \hspace{0.33cm}%
    \emptyset:=\ \left\{\text{alloced}:\emptyset,\text{freed}:\emptyset\right\}\\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc \mid \absev{Dealloc\ }\loc \mid \absev{Use\ }\loc \mid \absterm\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
  \typerule{tms-uninteresting}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
  }{tms-uninteresting}
  %
  \typerule{tms-abort}{
  }{
    \monitorcheck[]{\tmsmonitor}{\emptyset}{\absterm}
  }{tms-abort}
  %
  \typerule{tms-use}{
    \loc\in\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    \loc\notin\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\cup\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    \loc\in\tmsmonitor.\text{alloced} &
    \loc\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{alloced}: \tmsmonitor.\text{alloced}\setminus\left\{\loc\right\},\text{freed}: \tmsmonitor.\text{freed}\cup\left\{\loc\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc}
  }{tms-dealloc}
\end{center}
\begin{center}
  \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ with respect to \gls{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc}
  }{tms-alloc-authentic}
  %
  \typerule{tms-dealloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{tms-dealloc-authentic}
  %
  \typerule{tms-use-authentic}{
  }{
    \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
  }{tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{tms-branch-authentic}
  %
  \typerule{tms-binop-authentic}{
  }{
    \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{tms-binop-authentic}
  %
  \typerule{tms-empty-authentic}{
  }{
    \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{tms-empty-authentic}
  %
  \typerule{tms-abort-authentic}{
  }{
    \tmstraceagree[]{\lightning}{\absterm}
  }{tms-abort-authentic}
\end{center}
